Learning constraints in tabular data

### 2016-05-10 Paper/ECAI/tabular.tex
Reworked definitions a bit

The inverse problem is, given an assignment to all cells, to find the constraints that are present in the spreadsheet.
We define the {\bf Tabular Constraint Learning Problem} as follows:
%
\begin{definition} \textit{Tabular Constraint Learning.}\label{def:problem_statement}
  Given ${\cal G}$ a set of groups derived from fully instantiated tables ${\cal T}$ (all cells have values) and a set of {\template}s ${\cal C}$ ; find the set of all constraints $s(G_1', ..., G_n')$ that match the syntax of a \template in ${\cal C}$ and where the groups $G_1', ... , G_n'$ with $\forall i, G_i' \subseteq G_i, G_i \in {\cal G}$ satisfy both the signature and the definition of that \template.
\end{definition}
% {\bf Given }
% \begin{enumerate}
% \item
% a set of instantiated tables (so all cells have values) ${\cal T}$;
% \item
% a set of {\template}s ${\cal C}$;
% \item
% a set of groups ${\cal G}$ for the tables ${\cal T}$;
% \end{enumerate}
% \noindent
% {\bf Find}  the set of all constraints $s(G_1', ..., G_n')$ that 
% \begin{enumerate}
% \item are satisfied  in ${\cal T}$;
% \item for which all $G_i' \subseteq G_i \in {\cal G}$ ;
% \item the groups $G_1', ... , G_n'$ satisfy the signature of the constraint template~$s \in {\cal C}$.
% \end{enumerate}
An example solution for the type-consistent groups of the tables in Figure~\ref{fig:main_example} and {\template}'s in Table~\ref{table:constraints} is shown in Figure~\ref{fig:sol_example}.

@@

\begin{definition}[Condensed Tabular Constraint Learning]\label{def:condensed_problem_statement}
  Let ${\cal T}$ a set of instantiated tables (all cells have values),  ${\cal C}$ be a set of {\template}s,  ${\cal G}$ be a set of groups for the tables ${\cal T}$, \dependencies be the set of all specifity rules, then find the set of all constraints $s(G_1', ..., G_n')$ that are satisfied  in ${\cal T}$, for which all $G_i' \subseteq G_i \in {\cal G}$, the groups $G_1', ... , G_n'$ satisfy the signature of the constraint template~$s \in {\cal C}$ and there is no $s'$ in ${\cal C}$ such that $s'(G_h',\dots,G_k')$ holds (for $1 \leq h \leq k \leq n$) and  $s'$ is more specific than $s$ in \dependencies.
\end{definition}

>>>>

The inverse problem is, given an assignment to all cells, to find the constraints that are present in the spreadsheet.
We define the {\bf Tabular Constraint Learning Problem} as follows:
%
\begin{definition} \textit{Tabular Constraint Learning.}\label{def:problem_statement}\\
  Given ${\cal G}$ a set of groups over fully instantiated tables ${\cal T}$ (all cells have values) and a set of {\template}s ${\cal S}$: find the set of all constraints $s(G_1', ..., G_n')$ that match the syntax of a \template~$s \in {\cal S}$ and where the (sub)groups $G_1', ... , G_n'$ with $\forall i: G_i' \subseteq G_i, G_i \in {\cal G}$ satisfy both the signature and the definition of that \template.
\end{definition}
% {\bf Given }
% \begin{enumerate}
% \item
% a set of instantiated tables (so all cells have values) ${\cal T}$;
% \item
% a set of {\template}s ${\cal C}$;
% \item
% a set of groups ${\cal G}$ for the tables ${\cal T}$;
% \end{enumerate}
% \noindent
% {\bf Find}  the set of all constraints $s(G_1', ..., G_n')$ that 
% \begin{enumerate}
% \item are satisfied  in ${\cal T}$;
% \item for which all $G_i' \subseteq G_i \in {\cal G}$ ;
% \item the groups $G_1', ... , G_n'$ satisfy the signature of the constraint template~$s \in {\cal C}$.
% \end{enumerate}
An example solution for the type-consistent groups of the tables in Figure~\ref{fig:main_example} and {\template}'s in Table~\ref{table:constraints} is shown in Figure~\ref{fig:sol_example}.

@@

\begin{definition} \textit{Condensed Tabular Constraint Learning}\label{def:condensed_problem_statement}\\
  Given a set of instantiated tables~${\cal T}$ (all cells have values), a set of {\template}s~${\cal S}$, a set of groups~${\cal G}$ over the tables~${\cal T}$, and the set of all specifity rules~\dependencies: find the set of all constraints $s(G_1', ..., G_n')$ that are satisfied  in ${\cal T}$, for which all $G_i' \subseteq G_i \in {\cal G}$, the (sub)groups $G_1', ... , G_n'$ satisfy the signature of the constraint template~$s \in {\cal C}$ and there is no $s'$ in ${\cal C}$ such that $s'(G_h',\dots,G_k')$ holds (for $1 \leq h \leq k \leq n$) and  $s'$ is more specific than $s$ in \dependencies.
\end{definition}
